### 2010-03-29 papers/icfp-2010-desc/paper_desc.tex
Desc@ICFP: generic induction refers to Benke et al.

Whereas this definition is amply sufficient in the simply-typed world,
it comes short of its promises in the dependently-typed realm. Indeed,
this type is not dependent. As this operator will be the corner stone
of any inductive definition, we are better off sharpening it before use.

The first step consists in turning $\V{T}$ into a predicate
$\Bhab{\V{P}}{\Mu{\V{D}} \To \Set}$, hence introducing a dependency on the
descriptions. Consequently, we strengthen the algebra $\descop{\V{D}}{\V{T}}
\To \V{T}$ by a similar process. We start with turning the arrow into a
dependent arrow, hence offering $\Bhab{\V{xs}}{\descop{\V{D}}{(\Mu{\V{D}})}}$ to
further analysis.

>>>>

Whereas this definition is amply sufficient in the simply-typed world,
it comes short of its promises in the dependently-typed realm. Indeed,
this type is not dependent, being restricted to a notion of
\emph{iteration}. As this operator will be the corner stone of any
inductive definition, we are better off sharpening it before use.

The first step consists in turning $T$ into a predicate
$\Bhab{P}{\Mu{D} \To \Set}$, hence introducing a dependency on the
descriptions. Consequently, we strengthen the algebra $\descop{D}{T}
\To T$ by a similar process. We start with turning the arrow into a
dependent arrow, hence offering $\Bhab{xs}{\descop{D}{(\Mu{D})}}$ to
further analysis.
